Teoria das Categorias \\ Flechas e Mónades \\ em Java

### 2015-09-19 paper/main.tex
Fixed multiple numbering issues found in footmarkers pointing to same footnotes.

% libraries preamble
\usepackage[numbers,sort&compress,square]{natbib}
\usepackage{listings}
\usepackage{lipsum}
\usepackage[T1]{fontenc}
\usepackage[portuguese]{babel}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage[svgnames]{xcolor}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{caption}
\usepackage{hyperref}

@@

\begin{lstlisting}[caption={Type class para funtores\protect\footnotemark\label{fnt:type-class-funtor}}, style=haskell-style, label={lst:type-class-functor}]
class Functor f where  
    fmap :: (a -> b) -> f a -> f b

instance Functor Maybe where  
    fmap f (Just x) = Just (f x)  
    fmap f Nothing  = Nothing
\end{lstlisting}
\footnotetext{Fonte: M. Lipovaca,~\textit{Learn You a Haskell for Great Good!: A Beginner's Guide}, 2011.\label{fnt:type-class-funtor}}

@@

\begin{lstlisting}[caption={Função fmap para Maybe\protect\footnotemark\label{fnt:type-class-funtor}}, style=haskell-style, label={lst:fmap-maybe}]
fmap (*2) (Just 200)  
\end{lstlisting}

>>>>

% libraries preamble
\usepackage[numbers,sort&compress,square]{natbib}
\usepackage{listings}
\usepackage{lipsum}
\usepackage[T1]{fontenc}
\usepackage[portuguese]{babel}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage[svgnames]{xcolor}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{scrextend}

@@

\begin{lstlisting}[caption={Type class para funtores\protect\footref{fnt:type-class-funtor}}, style=haskell-style, label={lst:type-class-functor}]
class Functor f where  
    fmap :: (a -> b) -> f a -> f b

instance Functor Maybe where  
    fmap f (Just x) = Just (f x)  
    fmap f Nothing  = Nothing
\end{lstlisting}

\footnote{Fonte: M. Lipovaca,~\textit{Learn You a Haskell for Great Good!: A Beginner's Guide}, 2011.\label{fnt:type-class-funtor}}

@@

\begin{lstlisting}[caption={Função fmap para Maybe\protect\footref{fnt:type-class-funtor}}, style=haskell-style, label={lst:fmap-maybe}]
fmap (*2) (Just 200)  
\end{lstlisting}
